---
title: "assumptionChecking"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    number_sections: true
    theme: simplex 
---

``` {r setup, include=TRUE, cache = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(dplyr)
library(GGally)
library(leaps)
library(ggfortify)
```

```{r, message = FALSE}
data = read.table("winequality-red.csv", sep=";", header=T)

```

# ALCOHOL VS QUALITY

## Linearity
```{r}
lm1 = lm(quality ~ alcohol, data = data)
par(cex = 0.5)
plot(quality ~ alcohol, data = data)
abline(lm1, lwd = 3, col = 'red')
```

## Residuals and Normalitys
```{r}
autoplot(lm1, which = 1:2)
```

# SULFATES VS QUALITY
```{r}
# SULPHATES LINEARITY
lm1 = lm(quality ~ sulphates, data = data)
par(cex = 0.5)
plot(quality ~ sulphates, data = data)
abline(lm1, lwd = 3, col = 'red')
```

## Residuals and Normalitys
```{r}
autoplot(lm1, which = 1:2)
```

# VOLATILE ACIDITY VS QUALITY
```{r}
# VOLATILE ACIDITY LINEARITY
lm1 = lm(quality ~ volatile.acidity, data = data)
par(cex = 0.5)
plot(quality ~ volatile.acidity, data = data)
abline(lm1, lwd = 3, col = 'red')
```

## Residuals and Normalitys
```{r}
autoplot(lm1, which = 1:2)
```

# TOTAL SULFUR DIOXIDE VS QUALITY
```{r}
# TOTAL SULFUR DIOXIDE LINEARITY
lm1 = lm(quality ~ total.sulfur.dioxide, data = data)
par(cex = 0.5)
plot(quality ~ total.sulfur.dioxide, data = data)
abline(lm1, lwd = 3, col = 'red')
```

## Residuals and Normalitys
```{r}
autoplot(lm1, which = 1:2)
```

# FREE SULFUR DIOXIDE VS QUALITY
```{r}
# FREE SULFUR DIOXIDE LINEARITY
lm1 = lm(quality ~ free.sulfur.dioxide, data = data)
par(cex = 0.5)
plot(quality ~ free.sulfur.dioxide, data = data)
abline(lm1, lwd = 3, col = 'red')
```
## Residuals and Normalitys
```{r}
autoplot(lm1, which = 1:2)
```

# CHLORIDES VS QUALITY
```{r}
# CHLORIDES LINEARITY
lm1 = lm(quality ~ chlorides, data = data)
par(cex = 0.5)
plot(quality ~ chlorides, data = data)
abline(lm1, lwd = 3, col = 'red')
```

## Residuals and Normalitys
```{r}
autoplot(lm1, which = 1:2)
```

# PH VS QUALITY
```{r}
# pH LINEARITY
lm1 = lm(quality ~ pH, data = data)
par(cex = 0.5)
plot(quality ~ pH, data = data)
abline(lm1, lwd = 3, col = 'red')
```

## Residuals and Normalitys
```{r}
autoplot(lm1, which = 1:2)
```

# CITRIC ACID VS QUALITY
```{r}
# citric.acid LINEARITY
lm1 = lm(quality ~ citric.acid, data = data)
par(cex = 0.5)
plot(quality ~ citric.acid, data = data)
abline(lm1, lwd = 3, col = 'red')
```

## Residuals and Normalitys
```{r}
autoplot(lm1, which = 1:2)
```

# RESIDUAL SUGAR VS QUALITY
```{r}
# residual.sugar LINEARITY
lm1 = lm(quality ~ residual.sugar, data = data)
par(cex = 0.5)
plot(quality ~ residual.sugar, data = data)
abline(lm1, lwd = 3, col = 'red')
```

## Residuals and Normalitys
```{r}
autoplot(lm1, which = 1:2)
```

# FIXED.ACIDITY VS QUALITY
```{r}
# fixed.acidity LINEARITY
lm1 = lm(quality ~ fixed.acidity, data = data)
par(cex = 0.5)
plot(quality ~ fixed.acidity, data = data)
abline(lm1, lwd = 3, col = 'red')
```
## Residuals and Normalitys
```{r}
autoplot(lm1, which = 1:2)
```

# DENSITY VS QUALITY
```{r}
# density LINEARITY
lm1 = lm(quality ~ density, data = data)
par(cex = 0.5)
plot(quality ~ density, data = data)
abline(lm1, lwd = 3, col = 'red')
```

## Residuals and Normalitys
```{r}
autoplot(lm1, which = 1:2)
```