---
title: "assumptionChecking"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    number_sections: true
    theme: simplex 
---

``` {r setup, include=TRUE, cache = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(dplyr)
library(GGally)
library(leaps)
library(ggfortify)
library(ggthemes)
library(ggcharts)
```

```{r, message = FALSE}
data = read.table("winequality-red.csv", sep=";", header=T)

```

```{r}
#GGplot template scatter
data %>% ggplot() + aes(x=alcohol,y=quality) + geom_point(size =1) + theme_minimal() + ggtitle("Red wine quality vs Alcohol Percentage")+ xlab("Alcohol Percentage") + ylab("Red wine quality") + geom_smooth(method='lm', se=FALSE) 

##GGplot template residual 

```

# ALCOHOL VS QUALITY

## Linearity
```{r}
lm1 = lm(quality ~ alcohol, data = data)
par(cex = 0.5)
plot(quality ~ alcohol, data = data)
abline(lm1, lwd = 3, col = 'red')

data %>% ggplot() + aes(x=alcohol,y=quality) + geom_point(size =1) + theme_minimal() + ggtitle("Red wine quuality vs Alcohol Percentage")+ xlab("Alcohol Percentage") + ylab("Red wine quality") + geom_smooth(method='lm', se=FALSE) 
```

## Residuals and Normalitys
```{r}
autoplot(lm1, which = 1:2) + theme_minimal() 
```

# SULFATES VS QUALITY
```{r}
# SULPHATES LINEARITY
lm1 = lm(quality ~ log(sulphates, 30), data = data)
par(cex = 0.5)
plot(quality ~ log(sulphates, 30), data = data)
abline(lm1, lwd = 3, col = 'red')

data %>% ggplot() + aes(x=log(sulphates),y=quality) + geom_point(size =1) + theme_minimal() + ggtitle("Red wine quality vs Log of Sulphate Concentration")+ xlab("Sulphate Concentration") + ylab("Red wine quality") + geom_smooth(method='lm', se=FALSE) 
```

## Residuals and Normalitys
```{r}
autoplot(lm1, which = 1:2)
```

# VOLATILE ACIDITY VS QUALITY
```{r}
# VOLATILE ACIDITY LINEARITY
lm1 = lm(quality ~ log(sqrt((volatile.acidity))), data = data)
par(cex = 0.5)
plot(quality ~ log(sqrt((volatile.acidity))), data = data)
abline(lm1, lwd = 3, col = 'red')

data %>% ggplot() + aes(x=alcohol,y=quality) + geom_point(size =1) + theme_minimal() + ggtitle("Red wine quuality vs Alcohol Percentage")+ xlab("Alcohol Percentage") + ylab("Red wine quality") + geom_smooth(method='lm', se=FALSE) 
```

## Residuals and Normalitys
```{r}
autoplot(lm1, which = 1:2)
```

# TOTAL SULFUR DIOXIDE VS QUALITY
```{r}
# TOTAL SULFUR DIOXIDE LINEARITY
lm1 = lm(quality ~ log(total.sulfur.dioxide), data = data)
par(cex = 0.5)
plot(quality ~ log(total.sulfur.dioxide), data = data)
abline(lm1, lwd = 3, col = 'red')
```

## Residuals and Normalitys
```{r}
autoplot(lm1, which = 1:2)
```

# FREE SULFUR DIOXIDE VS QUALITY
```{r}
# FREE SULFUR DIOXIDE LINEARITY
lm1 = lm(quality ~ free.sulfur.dioxide, data = data)
par(cex = 0.5)
plot(quality ~ free.sulfur.dioxide, data = data)
abline(lm1, lwd = 3, col = 'red')
```
## Residuals and Normalitys
```{r}
autoplot(lm1, which = 1:2)
```

# CHLORIDES VS QUALITY
```{r}
# CHLORIDES LINEARITY
lm1 = lm(quality ~ chlorides, data = data)
par(cex = 0.5)
plot(quality ~ chlorides, data = data)
abline(lm1, lwd = 3, col = 'red')
```

## Residuals and Normalitys
```{r}
autoplot(lm1, which = 1:2)
```

# PH VS QUALITY
```{r}
# pH LINEARITY
lm1 = lm(quality ~ I(pH^2), data = data)
par(cex = 0.5)
plot(quality ~ I(pH^2), data = data)
abline(lm1, lwd = 3, col = 'red')
```

## Residuals and Normalitys
```{r}
autoplot(lm1, which = 1:2)
```

# CITRIC ACID VS QUALITY
```{r}
# citric.acid LINEARITY
lm1 = lm(quality ~ citric.acid, data = data)
par(cex = 0.5)
plot(quality ~ citric.acid, data = data)
abline(lm1, lwd = 3, col = 'red')
```

## Residuals and Normalitys
```{r}
autoplot(lm1, which = 1:2)
```

# RESIDUAL SUGAR VS QUALITY
```{r}
# residual.sugar LINEARITY
lm1 = lm(quality ~ residual.sugar, data = data)
par(cex = 0.5)
plot(quality ~ residual.sugar, data = data)
abline(lm1, lwd = 3, col = 'red')
```

## Residuals and Normalitys
```{r}
autoplot(lm1, which = 1:2)
```

# FIXED.ACIDITY VS QUALITY
```{r}
# fixed.acidity LINEARITY
lm1 = lm(quality ~ fixed.acidity, data = data)
par(cex = 0.5)
plot(quality ~ fixed.acidity, data = data)
abline(lm1, lwd = 3, col = 'red')
```
## Residuals and Normalitys
```{r}
autoplot(lm1, which = 1:2)
```

# DENSITY VS QUALITY
```{r}
# density LINEARITY
lm1 = lm(quality ~ density, data = data)
par(cex = 0.5)
plot(quality ~ density, data = data)
abline(lm1, lwd = 3, col = 'red')
```

## Residuals and Normalitys
```{r}
autoplot(lm1, which = 1:2)
```