---
title: "Determining Risk Factors Associate With Red Wine"
subtitle: "DATA2002 Group Presentation"
author: "Authors"
output:
  xaringan::moon_reader:
    css: ["default", "assets/sydney-fonts.css", "assets/sydney.css"]
    self_contained: false 
    seal: true 
    nature:
      beforeInit: ["assets/remark-zoom.js", "https://platform.twitter.com/widgets.js"]
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9' 
      navigation:
        scroll: false # disable slide transitions by scrolling
---

```{r}
install.packages("systemfonts")
```

```{r load_refs, echo=FALSE, cache=FALSE, message=FALSE}
library(RefManageR)

library(tidyverse)
library(GGally)
library(car)
library(ggfortify)
library(sjPlot)
library(equatiomatic)
library(faraway)
library(qtlcharts)
library(ggfortify)
library(caret)
knitr::opts_chunk$set(echo = FALSE)
```
BibOptions(check.entries = FALSE, 
            bib.style = "authoryear",
            cite.style = 'authoryear', 
            style = "markdown",
            hyperlink = FALSE, 
            dashed = FALSE)
 myBib <- ReadBib("assets/example.bib", check = FALSE)
## Background 
---
## Introduction 
- Aim
- Method
 
---
## Dataset 


```{r, echo = FALSE, results = 'hide', message=FALSE, warning=FALSE}
table60 <- matrix(c("Measure of the tartaric, malic, citric and succinic in grapes", "fatty acids in wine which contribute to a distasteful vinegar flavour in the wine", "Manipulated to increase flavour", "Raw sugar derived from grapes (post fermentation). Higher residual sugar = Sweeter Wine", "Impacts on saltiness of the wine", "Sulphur Dioxide that has not yet reacted. Stops product from reacting to oxygen (causes browing and oxidation","Free Sulphur Dioxide + amount of SO2 in chemicals which are included in the wine", "Higher Density = better quality (expand on idea)", "Measure of the acidity. Lower pH = less susceptible to bacteria growth + increased flavour", "Introduced to protect against bacteria", "Concentration of alcohol in final product, impacts on flavour massively", "Summary of results of previous eleven variables"), ncol=1, byrow=TRUE)

colnames(table60) <- c('Description of Variable')
rownames(table60) <- c("Fixed Acidity", "Volatile Acidity", "Citric Acid", "Residual Sugar", "Chlorides", "Free Sulphur Dioxide","Total Sulphur Dioxide", "Density", "pH", "Sulphates", "Alcohol", "Quality")
table20 <- as.table(table60)
table20
```

```{r, echo = FALSE}
install.packages("kable_styling")
table20 %>% 
  kbl(caption = "<center><strong>Analysis of Wine Quality Variables", allign = "c") %>% 
  kable_styling("striped")
```


---


## Assumptions Checking 
- Linearity 
---
## Assumptions Checking 
- Independence 
---
## Assumptions Checking 
- Homoskedasticity 
---
## Assumptions Checking 
- Normality 
---
## Analysis 
- Selecting appropriate model 
- Backward 
- Forward 
---
## Results
---
## Discussion
---
## Conclusion






