---
title: "Executive Summary Content"
output: html_document
---


---
title: "Lab Report 1"
output: html_document
---

Executive Summary

The data set which our group will be exploring highlights different factors which contribute to an overall quality rating of the Portugese red wine “Vinho Verde”. The first of the 12 variables is the fixed acidity. 

The fixed acidity is a measure of the tartaric, malic, citric and succinic, found within grapes, which are measured by a steam distillation of a sample of the wine. 

The volatile acidity (being the second variable) however measures the acetic acid levels in the wine which impacts on the flavour of the wine negatively if the acetic acid is too high. 

The third variable is citric acid which is used in wine in order to assist in increasing flavour by in turn increasing acidity. In analysying our data we should therefore find a correlation between citric acid and ___ acidity. 

Moving away from acidity now, the data set analyses the residual sugars in “Vinho Verde”. The residual sugar in wines is not the artificially added sugars, but the raw sugar from grapes found post fermentation, with higher levels of residual sugar unsurprisingly resulting in sweeter wine. (describe the red wine not very sweet????????). 

Chlorides are used in this data set as a factor contributing towards an overall rating for the wine due to its impact on the saltiness of the final product. 

The density of wine is deemed to be a major contributer to the overall quality of wine, with higher density resulting in higher quality (need to elaborate on why?). 

pH is simply used in wine making in order to “determine ripeness in relation to acidity”. Lower pH is far more desirable as it reduces susceptibility to bacteria growth, while also increasing the quality of taste by making the final product “tart and crisp”. 

Sulphate levels is the next criteria the researchers used to determine overall wine quality rankings, with the sulphate being used in wine in order to protect the final product from bacteria. 

Evidently, alcohol concentration is a major contributing factor towards the final quality of “Vinho Verde”, with it having a large impact on flavour and desirability for the intended market. Finally, the final quality ranking summarises all of the previous factors into a final value. 



```{r}
table <- matrix(c("Fixed Acidity", "Description of Fixed Acidity", "Volatile Acidity", "Description of Volatile Acidity", "Citric Acid", "Description of Citric Acid", "Residual Sugar", "Description of Residual Sugar", "Chlorides", "Description of Chlorides", "Free Sulphur Dioxide", "Description of Free Sulphur Dioxide", "Total Sulphur Dioxide", "Description of Total Sulphur Dioxide", "Density", "Description of Density", "pH", "Description of pH", "Sulphates", "Description of Sulphates", "Alcohol", "Description of Alcohol", "Quality", "Description of Quality"), ncol=2, byrow=TRUE)
colnames(table) <- c('Variable','Description of Variable')
rownames(table) <- NULL
table2 <- as.table(table)
table2
library(kableExtra)
table2 %>% 
  kbl(caption = "<center><strong>Analysis of Wine Quality Variables", allign = "c") %>% 
  kable_styling("striped")

```
wef
wq


bh;bib


```{r}
table60 <- matrix(c("Measure of the tartaric, malic, citric and succinic in grapes", "fatty acids in wine which contribute to a distasteful vinegar flavour in the wine", "Manipulated to increase flavour", "Raw sugar derived from grapes (post fermentation). Higher residual sugar = Sweeter Wine", "Impacts on saltiness of the wine", "Sulphur Dioxide that has not yet reacted. Stops product from reacting to oxygen (causes browing and oxidation","Free Sulphur Dioxide + amount of SO2 in chemicals which are included in the wine", "Higher Density = better quality (expand on idea)", "Measure of the acidity. Lower pH = less susceptible to bacteria growth + increased flavour", "Introduced to protect against bacteria", "Concentration of alcohol in final product, impacts on flavour massively", "Summary of results of previous eleven variables"), ncol=1, byrow=TRUE)

colnames(table60) <- c('Description of Variable')
rownames(table60) <- c("Fixed Acidity", "Volatile Acidity", "Citric Acid", "Residual Sugar", "Chlorides", "Free Sulphur Dioxide","Total Sulphur Dioxide", "Density", "pH", "Sulphates", "Alcohol", "Quality")
table20 <- as.table(table60)
table20
library(kableExtra)
table20 %>% 
  kbl(caption = "<center><strong>Analysis of Wine Quality Variables", allign = "c") %>% 
  kable_styling("striped")
```
```{r}
abc =2 

```

abcfsadadhkk


,,,
