\begin{thebibliography}{3}
\newcommand{\enquote}[1]{``#1''}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\providecommand{\urlprefix}{URL }
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
  \providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
  \urlstyle{rm}\Url}\fi
\providecommand{\eprint}[2][]{\url{#2}}

\bibitem[{Allaire \emph{et~al}(2017)Allaire, {R Foundation}, Wickham, {Journal
  of Statistical Software}, Xie, Vaidyanathan, {Association for Computing
  Machinery}, Boettiger, {Elsevier}, Broman, Mueller, Quast, Pruim, Marwick,
  Wickham, Keyes, and Yu}]{CRAN:rticles}
Allaire J, {R Foundation}, Wickham H, {Journal of Statistical Software}, Xie Y,
  Vaidyanathan R, {Association for Computing Machinery}, Boettiger C,
  {Elsevier}, Broman K, Mueller K, Quast B, Pruim R, Marwick B, Wickham C,
  Keyes O, Yu M (2017).
\newblock \emph{rticles: Article Formats for R Markdown}.
\newblock R package version 0.4.1,
  \urlprefix\url{https://CRAN.R-project.org/package=rticles}.

\bibitem[{MacFarlane J (2017)}]{pandoc}
MacFarlane J (2017).
\newblock \emph{Pandoc: A Universal Document Converter}.
\newblock Version 1.19.2.1, \urlprefix\url{http://pandoc.org}.

\bibitem[{Xie Y (2017)}]{}
Xie Y (2017).
\newblock \emph{knitr: A General-Purpose Package for Dynamic Report Generation
  in R}.
\newblock R package version 1.17, \urlprefix\url{https://yihui.name/knitr/}.

\bibitem[{Wickham et al., (2019)}]{}
Wickham et al., (2019).
\newblock \emph{Welcome to the tidyverse. Journal of Open
Source Software, 4(43), 1686}.
\newblock \urlprefix\url{https://doi.org/10.21105/joss.01686}.

\bibitem[{McLean MW(2017)}]{}
McLean MW (2017).
\newblock \emph{RefManageR: Import and Manage BibTeX and BibLaTeX
References in R. The Journal of Open Source Software}.
\newblock \urlprefix\url{https://doi.org/10.21105/joss.00338}.

\bibitem[{McLean MW (2014)}]{}
McLean MW (2014).
\newblock \emph{Straightforward Bibliography Management in R
Using the RefManager Package. arXiv: 1403.2036 [cs.DL]{}}.
\newblock \urlprefix\url{https://arxiv.org/abs/1403.2036}.

\bibitem[{Schloerke B, Cook D, Larmarange J, Briatte F,
Marbach M, Thoen E, Elberg T and Crowley J (2021)}]{}
Schloerke B, Cook D, Larmarange J, Briatte F,
Marbach M, Thoen E, Elberg T and Crowley J (2021).
\newblock \emph{GGally: Extension to ggplot2}.
\newblock R package version 2.1.2. \urlprefix\url{https://CRAN.R-project.org/package=GGally}.

\bibitem[{Fox J and Weisberg S (2019)}]{}
Fox J and Weisberg S (2019).
\newblock \emph{R Companion to Applied
Regression, Third Edition. Thousand Oaks CA: Sage}.
\newblock \urlprefix\url{https://socialsciences.mcmaster.ca/jfox/Books/Companion/}.

\bibitem[{Tang Y, Horijoshi M and Li W (2016)}]{}
Tang Y, Horijoshi M and Li W (2016)
\newblock \emph{ggfortify: Unified
Interface to Visualize Statistical Result of Popular R Packages}.
\newblock The R Journal 8.2 (2016): 478-489.

\bibitem[{Lüdecke D (2021)}]{}
Lüdecke D (2021)
\newblock \emph{sjPlot: Data Visualization for Statistics in
Social Science}.
\newblock R package version 2.8.9 \urlprefix\url{https://CRAN.R-project.org/package=sjPlot}.

\bibitem[{Anderson D, Heiss A, Sumners J (2021)}]{}
Anderson D, Heiss A, Sumners J (2021).
\newblock \emph{equatiomatic: Transform Models into LaTeX Equations}.
\newblock R package version 0.3.0 \urlprefix\url{https://CRAN.R-project.org/package=equatiomatic}.

\bibitem[{Faraway J (2016)}]{}
Faraway J (2016).
\newblock \emph{faraway: Functions and Datasets for Books}.
\newblock R package version 1.0.7 \urlprefix\url{https://CRAN.R-project.org/package=faraway}.

\bibitem[{Broman K(2015)}]{}
Broman K (2015).
\newblock \emph{R/qtlcharts: interactive graphics for
quantitative trait locus mapping}.
\newblock \urlprefix\url{doi:10.1534/genetics.114.172742}.

\bibitem[{Kuhn M (2021)}]{}
Kuhn M (2021).
\newblock \emph{caret: Classification and Regression Training}.
\newblock R package version 6.0-90. \urlprefix\url{https://CRAN.R-project.org/package=caret}.

\bibitem[{Zhu H (2021)}]{}
Zhu H (2021).
\newblock \emph{ableExtra: Construct Complex Table with 'kable' and Pipe Syntax}.
\newblock R package version 1.3.4. \urlprefix\url{https://CRAN.R-project.org/package=kableExtra}..

\bibitem[{Firke S (2021)}]{}
Firke S (2021).
\newblock \emph{Janitor: Simple Tools for Examining and Cleaning Dirty Data}.
\newblock R package version 2.1.0. \urlprefix\url{https://CRAN.R-project.org/package=janitor}.

\bibitem[{Wickham H, François R, Henry L and Müller K (2021)}]{}
Wickham H, François R, Henry L and Müller K (2021).
\newblock \emph{dplyr: A Grammar of Data Manipulation}.
\newblock R package version 1.0.7. \urlprefix\url{https://CRAN.R-project.org/package=dplyr}.

\bibitem[{Lumley T(2020)}]{}
Lumley T(2020).
\newblock \emph{leaps: Regression Subset Selection}.
\newblock  R package version 3.1.0. \urlprefix\url{https://CRAN.R-project.org/package=leaps}.

\bibitem[{Tarr G (2021)}]{}
Tarr G (2021).
\newblock \emph{Week three Lecture L08: Testing for independence – who was more likely to die on the Titanic?}.
\newblock [Powerpoint Slides]{}. DATA2002, University of Sydney, Sydney, Australia. 

\bibitem[{Tarr G (2021)}]{}
Tarr G (2021).
\newblock \emph{Week eleven Lecture L26: Simple linear regression}.
\newblock [Powerpoint Slides]{}. DATA2002, University of Sydney, Sydney, Australia. 

\bibitem[{Tarr G (2021)}]{}
Tarr G (2021).
\newblock \emph{Week eleven Lecture L27: Multiple regression and model selection}.
\newblock [Powerpoint Slides]{}. DATA2002, University of Sydney, Sydney, Australia. 

\bibitem[{Tarr G (2021)}]{}
Tarr G (2021).
\newblock \emph{Week eleven Lecture L28: Prediction internals and performance assessment}.
\newblock [Powerpoint Slides]{}. DATA2002, University of Sydney, Sydney, Australia. 

\bibitem[{Tarr G (2021)}]{}
Tarr G (2021).
\newblock \emph{Week ten Live Lecture}.
\newblock [Video file]{}. DATA2002, University of Sydney, Sydney, Australia. 

\bibitem[{Tarr G (2021)}]{}
Tarr G (2021).
\newblock \emph{Week eleven Live Lecture}.
\newblock [Video file]{}. DATA2002, University of Sydney, Sydney, Australia. 

\end{thebibliography}
