---
title: Executive Summary - DATA2002 Assignment 2

# Use letters 'a', 'b', ... or digits '1', '2', ... for different
# affiliations and addresses. Use '~' or '""' to suppress the
# display of the affiliation and address.
author:
  - name: 500520320, 480025267, 500505430, 500586901, 500555424
address:
    address: University of Sydney

# Optional: line of arbitrary text with additional information.
# Could be used, for example, to mention the bibliographic info in a post-print.
# If not specified, defaults to "This version was compiled on \today"
#date_subtitle: Published in *Journal of Statistical Software*, 2018

# For footer text  TODO(fold into template, allow free form two-authors)
lead_author_surname: 500520320, 480025267, 500505430, 500586901, 500555424

# Place DOI URL or CRAN Package URL here
doi_footer: "https://github.sydney.edu.au/epro3000/LAB-03-CC_early_8"

# Abstract
abstract: |
  The following paper analyses the quality of Vinho Verde red wine from Northern Portugal, measured from a scale of one to ten. Using multiple regression, this paper aims to model the quality of various red wines on other factors such as the alcohol concentration or total sulfur dioxide concentration. Various potential predictor variables were removed from the model for not meeting key assumption criteria such as co-linearity with red wine quality, normality, or residual homoscedasticity. Transformations were attempted on variables that didn’t meet the co-linearity assumption, with the only successful transformation being the log of total sulfur dioxide. Multiple regression was then computed using both a step-back and step-forward AIC-based model. These both netted the same model; a regression of red wine quality against alcohol concentration, volatile acidity, the log of total sulfur dioxide and density. In-sample performance of this model showcased an $R^2$ value of 0.32, indicating that the model may not be particularly strong, and an RMSE of 0.669. Performing 10-fold cross validation suggested that our selected model wasn’t subject to obvious overfitting issues. The model generated was as follows:
  $$
  \mathbf{Quality = -22.22 + 0.32AC -0.67VA - 0.06log(TSD) + 23.31D}
  $$


# Optional: Acknowledgements
acknowledgements: |
   We gratefully acknowledge all the help from the
   [rticles](https://cran.r-project.org/package=rticles) package
   \citep{CRAN:rticles} which not only introduced us to the powerful
   [PNAS LaTeX](http://www.pnas.org/site/authors/latex.xhtml) style
   class, but also provided useful code templates to study in the
   other mode as the fine macros. The [pandoc](http://pandoc.org)
   document converter \citep{pandoc} is the much-admired driving force
   behind the document manipulation. Additionally, we acknowledge the fantastic
   support and teaching provided by G. Tarr and the DATA2002 team throughout the semester.

# Optional: One or more keywords
#keywords:
#  - pdf
#  - vignette

# Paper size for the document, values of letter and a4
papersize: letter

# Font size of the document, values of 9pt (default), 10pt, 11pt and 12pt
fontsize: 8pt

# Optional: Force one-column layout, default is two-column
#one_column: true

# Optional: Enables lineo mode, but only if one_column mode is also true
#lineno: true

# Optional: Enable one-sided layout, default is two-sided
#one_sided: true

# Optional: Enable section numbering, default is unnumbered
numbersections: true

# Optional: Specify the depth of section number, default is 5
secnumdepth: 3

# Optional: Bibliography 
#bibliography: pinp

# Optional: include-after
#include-after: somefile.tex

# Optional: Skip inserting final break between acknowledgements, default is false
skip_final_break: true

# Customize footer, eg by referencing the vignette
footer_contents: "LAB-03-CC_early_8"

# Optional: Enable a 'Draft' watermark on the document
#watermark: true

# Produce a pinp document
# 
# Other options that can be set here, shown with their defaults
#   keep_tex: TRUE
#   collapse: FALSE
#   citation_package: natbib
#
# Any other arguments to rmarkdown::pdf_document could be set 
# here as well
#
output:
  pinp::pinp:
    includes:
      after_body: bib.tex

  
# Required: Vignette metadata for inclusion in a package.
vignette: >
  %\VignetteIndexEntry{Introduction to pinp}
  %\VignetteKeywords{pinp,vignette}
  %\VignettePackage{pinp}
  %\VignetteEngine{knitr::rmarkdown}

---

# Introduction 
## `Backgroud`
This dataset highlights different factors which contribute to an overall quality rating
of the Portuguese red wine “Vinho Verde”. Red wine quality may be of interest to producers of wine who are trying to better understand the factors that contribute to overall quality, as well as consumers who are interested in specific characteristics of red wines from speciality regions such as Portugal. 

## `Dataset Overview`
The dataset had 1599 rows corresponding to different wine observations, and was collected in 2009 from “Vinho
Verde” wine in the north of Portugal.
The input variables presented to us were collected from chemical
tests, and consisted of fixed acidity, volatile acidity, citric acid,
residual sugar, chlorides, free sulfur dioxide, total sulfur dioxide,
density, pH, sulphates, and alcohol.
The output variable is the wine quality, graded on a scale of 0
to 10. This was determined by the median score of at least three
evaluations made by wine experts.

The first of the 12 variables is the fixed acidity. The fixed acidity is a measure of the tartaric, malic, citric and succinic, found within grapes, which are measured by a steam distillation of a sample of the wine. The volatile acidity (being the second variable) however measures the acetic acid levels in the wine which impacts on the flavour of the wine negatively if the acetic acid is too high. The third variable is citric acid which is used in wine in order to assist in increasing flavour by in turn increasing acidity. Moving away from acidity now, the data set analyses the residual sugars in “Vinho Verde”. The residual sugar in wines is not the artificially added sugars, but the raw sugar from grapes found post fermentation, with higher levels of residual sugar unsurprisingly resulting in sweeter wine. Chlorides are used in this data set as a factor contributing towards an overall rating for the wine due to its impact on the saltiness of the final product. The density of wine is deemed to be a major contributor to the overall quality of wine, with higher density resulting in higher quality. pH is simply used in wine making in order to “determine ripeness in relation to acidity”. Lower pH is far more desirable as it reduces susceptibility to bacteria growth, while also increasing the quality of taste by making the final product “tart and crisp”. Sulphate levels are the next criteria the researchers used to determine overall wine quality rankings, with the sulphate being used in wine in order to protect the final product from bacteria. Evidently, alcohol concentration is a major contributing factor towards the final quality of “Vinho Verde”, with it having a large impact on flavour and desirability for the intended market. Finally, the final quality ranking summarises all of the previous factors into a final value.

# Analysis 
## `Assumption Validation` 
Multiple regression relies upon four key assumptions:
1.	Linearity.
2.	Independence.
3.	Normality.
4.	Homoscedasticity.

For each of these assumptions, the individual relationships between the input variables and quality of wine must meet the assumptions themselves, as well as the final model, and thus were
checked individually for each input variable against the quality
of wine. For independence, collection methodologies were not
explicitly outlined in the dataset, however we can assume that
each wine was independent of each other for the purposes of this
report.

Linearity refers to how well the input variables can be linearly
mapped to the output variable. Violations included free sulphur
dioxide, fixed acidity and pH, the latter of which is shown as an
example here. [] is also shown as an example of meeting the
linearity assumption. Additionally, for any variable which violated the linearity assumptions, data transformations were attempted to
improve linearity. The only successful case of this was the log transformation of Total
Sulphur Dioxide, as it allowed for the multiple orders of magnitude of total sulphur dioxide to be better expressed linearly against wine quality. (FIgure xxx)

Normality refers to the fact
that residuals should be normally distributed. Violations included
residual sugar  which can be seen below, as compared to a normal
example of [].

Finally, homoscedasticity refers to the even distribution of the
residuals around the mean. Any fanning of the residuals suggests
heteroscedasticity, violating this assumption. Violations include
sulphates and chlorides as they displayed distinct residual distribution patterns. Variables which violated assumptions were excluded
from the dataset used to construct the model. As such, we were
left with alcohol, volatile acidity, the log of total sulphur dioxide,
density and citric acid as the remaining input variables which met
all assumptions.


```{r, fig.height = 1.8, fig.pos = '!h',out.extra = '', echo=FALSE, cache=FALSE, message=FALSE, warning = FALSE}
library(tidyverse)
library(GGally)
library(car)
library(ggfortify)
library(sjPlot)
library(equatiomatic)
library(faraway)
library(qtlcharts)
library(caret)
library(kableExtra)
library(janitor)
library(dplyr)
library(leaps)
library(grid)
library(gridExtra)
data = read.table("winequality-red.csv", sep=";", header=T)
dataNew = data.frame(data$quality, data$alcohol, data$volatile.acidity, data$total.sulfur.dioxide, data$citric.acid, data$density)
dataNew = dataNew %>%
  mutate(data.volatile.acidity = log(data.volatile.acidity))
dataNew = dataNew %>%
  mutate(data.total.sulfur.dioxide = log(data.total.sulfur.dioxide))

l = lm(quality ~ volatile.acidity, data=data)
g1 = autoplot(l, which=2) +
  theme_bw() +
  theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank()) +
  ggtitle("Q-Q Plot of Volatile Acidity vs Quality")


r = lm(quality ~ residual.sugar, data=data)
g2 = autoplot(r, which=2) +
  theme_bw() +
  theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank()) +
  ggtitle("Q-Q Plot of Residual Sugar vs Quality")

#grid.arrange(g1@plots[[1]], g2@plots[[1]], ncol = 2)
```

## `Model Selection`
Both step-forward and step-back AIC variable selection methods for building a multiple regression model of the quality of red wine came to the same conclusion as can be shown in table 1 and table 2 below. Of the predictor variables that were used to build the model, i.e. those that met the fundamental multiple regression assumptions outlined previously, only the predictors in the two tables were significant. Therefore, the combination of predictors we are using to predict the quality of red wine are the alcohol concentration, volatile acidity, total sulphur dioxide, and the density. 
 
Hence, our model is as follows:

$$
\mathbf{Quality = -22.22 + 0.32AC -0.67VA - 0.06log(TSD) + 23.31D}
$$
This model had an AIC of 3259.415, an $R^2$ of 0.32 and an RMSE of 0.669.

```{r, fig.pos = 'h', echo=FALSE, cache=FALSE, message=FALSE, warning = FALSE}

library(tidyverse)
library(GGally)
library(car)
library(ggfortify)
library(sjPlot)
library(equatiomatic)
library(faraway)
library(qtlcharts)
library(caret)
library(kableExtra)
library(janitor)
library(dplyr)
library(leaps)
library(grid)
library(gridExtra)
data = read.table("winequality-red.csv", sep=";", header=T)
dataNew = data.frame(data$quality, data$alcohol, data$volatile.acidity, data$total.sulfur.dioxide, data$citric.acid, data$density)
dataNew = dataNew %>%
  mutate(data.volatile.acidity = log(data.volatile.acidity))
dataNew = dataNew %>%
  mutate(data.total.sulfur.dioxide = log(data.total.sulfur.dioxide))

M0 = lm(data.quality ~ 1, data = dataNew)
M1 = lm(data.quality ~ ., data = dataNew)
MFull = lm(quality ~ ., data = data)
#round(summary(M1)$coef,3)

step.fwd.aic = step(M0, scope = list(lower = M0, upper = M1), direction = "forward", trace = FALSE)

summary_table = summary(step.fwd.aic)

summary_table$coefficients <- round(summary_table$coefficients, 2)
rownames(summary_table$coefficients) <-c("Intercept", "Alcohol Concentration", "Volatile Acidity", "Total Sulfur Dioxide", "Density")
x1 = kable(summary_table$coefficients,"latex", caption="Step-Forward Method",booktabs = T)


step.back.aic = step(M1, direction = "backward", trace = FALSE)
summary_table2 = summary(step.back.aic)

summary_table2$coefficients <- round(summary_table2$coefficients, 2)
rownames(summary_table2$coefficients) <-c("Intercept", "Alcohol Concentration", "Volatile Acidity", "Total Sulfur Dioxide", "Density")
x2 = kable(summary_table2$coefficients, "latex", caption="Step-Back Method",booktabs = T)

x1 %>% kable_styling(latex_options = "hold_position")
x2 %>% kable_styling(latex_options = "hold_position")
```

# Results & Discussion

## `In Sample Performance`
As stated, the selected model had an $R^2$ of 0.32 and an RMSE of 0.669. This means that approximately 32% of the total variance in red wine quality can be explained by our regression model. This isn’t particularly high, indicating this linear model may not be performing strongly. This could be due to the somewhat poor co-linearity observed with most predictor variables versus wine quality in this dataset. However, to ensure that our model isn’t subject to overfitting, we want to test it using out of sample performance.  

## `Out of Sample Performance`
Using the caret package, we performed a 10-fold cross validation. The purpose of this was to test how well our model with predictor variables of alcohol concentration, volatile acidity, the log of total sulphur dioxide and density performed out of sample. This method allows for error to only be judged based on performance on the testing subset of the original sample, such that our judgement on the performance of the model isn’t impacted by the data that was used to produce the model in the first place.
 
Using 10-fold cross validation, we divided our sample randomly into 10 folds, of which one was allocated to be the testing set, while the rest were training folds used to build the model using the significant predictor variables. This process was repeated 10 times, where a different fold would be the testing set each time. The $R^2$, root mean squared error and mean average error of each prediction, compared to the real value in the testing set was then computed.
 
The following graph shows the distribution of $R^2$, MAE and RMSE for each of the 10 total cross validations performed. We have compared the performance of three separate models. The ‘full’ model represents all of the potential predictors that were initially present in the red wine quality data frame – even those that didn’t meet assumptions such as linearity. The ‘selected’ model represents the predictor variables we chose that were outlined previously. Finally, the simple model was the regression of red wine quality using only alcohol concentration which was the most significant predictor.
 
The full model had a median $R^2$ of 0.35, which was higher than the median $R^2$ of both the selected and simple models. However, as the full model had predictors that violated assumptions, it is an inappropriate multiple regression model so we must take this result with a grain of salt. The higher $R^2$ is likely to do with the fact that the larger number of predictors used would result in overfitting of the data, and artificially increasing the $R^2$ even though the relationship between the wine quality and some of the predictors may not have been linear in the first place. In comparison, the median $R^2$ of our model was 0.32, which was higher than that of the simple model which was 0.23.  Interestingly, as the $R^2$ of our selected model on the training data was very similar to the $R^2$ during in-sample performance, it appears that our selected model didn’t suffer from overfitting.
 
Again, discounting the full model, the selected model had the lowest median MAE 0.527 and RMSE (0.671) of the models being compared, indicating that it performed better on the testing set of red wine quality compared to the simple model. (figure name)


## `Assumption Re-Validation`
Additionally, our multiple regression model was also checked against the key assumptions outlined previously – normality and homoscedasticity. The following figures show that there is no obvious fanning pattern in the residuals, indicating homoscedasticity, and that the residuals of the full model are also normally distributed.

## `Limitations`
This model has a few limitations. The linearity of most predictor variables against red wine quality, even after attempting transformations, wasn’t very clear and so we had to be generous when determining what met this assumption for the purpose of analysis. An $R^2$ of 0.32 for the selected model is fairly low, which indicates that the in-sample performance of the model isn’t particularly strong, even though it appears the model didn’t run into overfitting issues when performing 10-fold cross-validation
 
There is also not much information available on the data collection process, so we are unsure about whether the different observations are independent or not. For example, red wines from neighbouring regions may not be independent and the quality of wine could be influenced as such. This is an assumption we have had to make for the purpose of the analysis. 

# Conclusion 
Overall, we were able to model the quality of red wine by linear regression, using alcohol concentration, volatile acidity, log of total sulfur dioxide, and density. We determined from this that there was a positive relationship between wine quality and alcohol quantity as well as density, whereas a negative relationship was determined between wine quality and volatile acidity as well as total sulphur dioxide. 
 
This could be of interest to both consumers of wine who are interested in characteristics of wine that may determine quality, as well as producers who are trying to make wines of certain qualities at certain price ranges.  


# References


<!-- Acknowledgements, and References, are automatically typeset after this -->
